---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# runnonmem

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of runnonmem is to run NONMEM from R.

## Installation

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("FelicienLL/runnonmem")
```

## Example

First, define where is NONMEM is installed
```{r eval=FALSE}
library(runnonmem)
options(runnonmem_nmfe_location = "C:/nmXXXXX/util/nmfeXX.bat")
```

Then launch a run
```{r eval=FALSE}
#If the control stream is in the working directory, just execute
runnonmem("mod001.mod")

# Or specify the project directory apart
runnonmem("mod001.mod", "/my/working/directory")

# Or full path to model object
runnonmem(file = "C:/my/working/directory.mod001.mod")
```

## Development

I often need to run NONMEM with the snap of a finger, without opening Pirana or something else. So a long time ago I made some messy code to achieve that. Recently, I decided to clean it and I turned it into a small proper R package. Instead of keeping it for myself, here it is.
